---
title: "MergedAll"
author: "Nicole Davis-Brown"
date: "9/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libr
```{r}
library(ggplot2)
library(dplyr)
library(readxl)
library(here)
library(readr)
library(lubridate)
library(tidyverse)
library(maps)
```


```{r}
#avmedlistgasprod<-read_excel(here::here("AV_MedListPrice_GasProd.xlsx"))
```

```{r}
#view(avmedlistgasprod)
```


ggplot() + 
geom_line(data=Data1, aes(x=A, y=B), color='green') + 
geom_line(data=Data2, aes(x=C, y=D), color='red')

p3<-ggplot()+
  geom_point(data= TXMedCounty_ListPrice_2016_2,
             aes(TXMedCounty_ListPrice_2016_2$Date,TXMedCounty_ListPrice_2016_2$MedListedPrice))+
  geom_line(aes(GasProd2016Totals$`GasProd2016$month`, GasProd2016Totals$Totals))

geom_vline(aes(xintercept =as.numeric(pres2$start)),
    data = pres2,
    colour ="white" , alpha = .5
  )

```{r}
options(scipen = 999)
```

```{r}
p2<-ggplot()+
geom_smooth(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$MedListPriceAve), color='green')
labs(x=avmedlistgasprod$Date,y=avmedlistgasprod$MedListPriceAve)

```

```{r}
p2 + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.ticks = element_line(size = 1))
```


```{r}
p1<-ggplot()+
geom_smooth(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$GasProdAve), color='red')
```


```{r}
p1 + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.ticks = element_line(size = 1))
```


```{r}
ggplot()+
geom_smooth(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$GasProdAve))+
geom_smooth(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$MedListPriceAve))+
              facet_wrap(~avmedlistgasprod$DC)
```


```{r}
ggplot(avmedlistgasprod, aes(avmedlistgasprod$Date, avmedlistgasprod$GasProdAve, color = avmedlistgasprod$DC))+
  geom_point()
  
```

```{r}
ggplot(avmedlistgasprod, aes(avmedlistgasprod$Date, avmedlistgasprod$MedListPriceAve, color = avmedlistgasprod$DC))+
  geom_point()
```



p2<-ggplot()+
geom_smooth(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$MedListPriceAve), color='green')
labs(x=avmedlistgasprod$Date,y=avmedlistgasprod$MedListPriceAve)

```{r}
p3<-ggplot()+
geom_smooth(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$GasProdAve))+
  geom_point(data=avmedlistgasprod, aes(x=avmedlistgasprod$Date, y=avmedlistgasprod$MedListPriceAve), color = avmedlistgasprod$DC)

    
```

```{r}
p3 + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1)) + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1), 
    axis.ticks = element_line(size = 1)) +labs(x = "date", y = "averages")
```




```{r}
testmap<-map_data('county')
map<-ggplot()+
  geom_polygon(data= testmap,
                  aes(x = long, 
                  y = lat, 
                  group = group), 
                  color = "white", 
                  fill ="gray")

```


```{r}
print(map)
```

