---
title: "Nicole_Zillow_2"
author: "Nicole Davis-Brown"
date: "9/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Zillow_Oil&Gas"
author: "Nicole Davis-Brown"
date: "9/15/2019"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
library(readxl)
library(here)
library(readr)
```



```{r}
PivotDatesToRows_Oil_Gas<<- read_csv(here("PivotDatesToRows_Oil_Gas.csv"))
```


I found oil and gas production data for texas on Kaggle. I want to use it to show the trend in oil and gas production vs the trend in med listing prices. Caveat is only if there is a relationship. 



Used Tableau Prep to convert dates from columns to rows. Created a date column with date as value. Imported data
Show first few rows. This is based on Zillow time series data for County State Med Listing Prices, broken down by month.

```{r}
head(`PivotDatesToRows_Oil_Gas`)
```

Filtered my pivot table so I only see data for Texas

```{r}
TXMedCounty_ListPrice <- filter(PivotDatesToRows_Oil_Gas, PivotDatesToRows_Oil_Gas$State =="TX")
```


CHeck to make sure filter worked
```{r}
head(TXMedCounty_ListPrice)
```

Imported data set District Listings that I pulled from https://www.rrc.state.tx.us/about-us/organization-activities/rrc-locations/counties-by-dist/ 
I should probably check to make sure the districts were the same for the data time frame I am using. I will likely used most recent times to be sure.

merged district listing and TX med county price listings so that I could bring in the District #. I will need this when I plot my TX oil and gas production data. 



```{r}
District_Listings<-read_excel(here("District Listings.xlsx"))
```



```{r}
distric_Med_Merge <-merge(District_Listings,TXMedCounty_ListPrice,by='RegionName')
```

Checking to make sure the merge went well. 


```{r}
View(distric_Med_Merge)
```

I only want data from 2016 and 2017 and my skills are not yet great enough for the if/or/and so I did it in two grep funtions. 

```{r}
TXMedCounty_ListPrice_2016<-distric_Med_Merge[grep("^2016",distric_Med_Merge$Date),]
```


```{r}
TXMedCounty_ListPrice_2017<-distric_Med_Merge[grep("^2017",distric_Med_Merge$Date),]
```

Used rbind to add the two grep tables together

```{r}
TXmedCounty_ListPrice_2016_2017<-rbind(TXMedCounty_ListPrice_2017,TXMedCounty_ListPrice_2016)
```

checking results of rbind


```{r}
View(TXmedCounty_ListPrice_2016_2017)
```

```{r}
GasProd2016<-read_excel(here("GasProd_2016_Subset.xlsx"))
```

```{r}
GasProd2016 %>% group_by(GasProd2016$month, GasProd2016$monthly_type_well)%>%
summarise()
```
```{r}
GasProd2016Totals<-GasProd2016 %>%
 group_by(GasProd2016$district, GasProd2016$month) %>%
  summarise(Totals = sum(gas_production))
```


```{r}
head(GasProd2016Totals)
```


1st set of data is how I want so now I am playing with graphing which is NOT going well. I need to filter down and focus on a few dates or a few Counties etc.. But at least it is something. Once I get this nailed downs I will incorporate the oil and gas production plot to see how it looks. 

```{r}
ggplot(TXmedCounty_ListPrice_2016_2017,aes(Metro,County)) +
  geom_point(aes(color = Date))
```



```{r}
Sub2016<- filter(TXmedCounty_ListPrice_2016_2017,grepl("^2016",TXmedCounty_ListPrice_2016_2017$Date))
```

```{r}
View(Sub2016)
```

```{r}
subsep09 <- filter(TXmedCounty_ListPrice_2016_2017,Date %in% c("2016-09", "2016-11"))
```

```{r}
View(subsep09)
```


Remove variable or various object
```{r echo=FALSE}
rm()
```
